Supporting Information

### 2018-04-01 SupportingInformation.Rmd
filled in fig description for count and ff results in .Rmd and minor plot label change in .R

### Non-paramtric analysis of tail dependence \label{Ex_count_NPA}

@@

@@

<!--Shya, can you please organize these following plots into one plot with mutliple panels? Once that is done, please add some text describing these results.-->
\begin{figure}[!h]
\begin{center}
\textbf{\;\;\;\;\;\;\;\ (A) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (B)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Kendall_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (C) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (D)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Corl-Coru_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Pl-Pu_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (E)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_D2u-D2l_vs_D.pdf}
\caption{Results for Aphid-count}
\end{center}\label{fig_aphid_count}
\end{figure}

@@

The model-averaged (averaging performed using AIC weights) lower-tail dependence statistic and 
the model-averaged (again, AIC based) upper-tail dependence statistic are in 
Tables \ref{tab_ff_LTdep_AICw} and \ref{tab_ff_UTdep_AICw}, respectively. These values were exclusively positive, thereby differing from what a normal copula would give (i.e., $0$), and answering the second part of question 1 for these data - these data have greater tail dependence (lower and upper) than would be expected from a normal-copula nul hypothesis.

@@

Mean values of our statistics ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_l$, $\Dsq_u$, 
$\cor_l-\cor_u$, $\Ps_l-\Ps_u$, $\Dsq_u-\Dsq_l$), as well as mean Kendall and Spearman 
correlations, were 
computed across all pairs of sampling locations, and confidence intervals of these means were 
computed via a spatial
resampling scheme, as described in Methods (Table \ref{tab_count_resamp}).
Confidence intervals of
$\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_l$, and $\Dsq_u$ always excluded 
zero and mean values were positive,
indicating tail dependence.
Confidence intervals of $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, $\Dsq_u-\Dsq_l$ also always 
exluded $0$ and were negative, indicating asymmetry of tail dependence, a feature 
that data with normal copula 
structure do not have, providing further evidence answering the third part of question 1.
The contrast here with the analogous results for abundances of the green spruce aphid is 
again illuminating.

@@

<!--Shya, can you please organize these following plots into one plot with mutliple panels? Once that is done, please add some text describing these results.-->
\begin{figure}[!h]
\begin{center}
\textbf{\;\;\;\;\;\;\;\ (A) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (B)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Spearman_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Kendall_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (C) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (D)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl-Coru_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl-Pu_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (E)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u-D2l_vs_D.pdf}
\caption{Results for Aphid-ff}
\end{center}\label{fig_aphid_ff}
\end{figure}

>>>>

### Non-parametric analysis of tail dependence \label{Ex_count_NPA}

@@

<!--Shya, can you please organize these following plots into one plot with mutliple panels? Once that is done, please add some text describing these results.-->
\begin{figure}[!h]
\begin{center}
\textbf{\;\;\;\;\;\;\;\ (A) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (B)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Spearman_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Kendall_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (C) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (D)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Corl-Coru_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_Pl-Pu_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (E)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_count/Sp_10_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for green spruce aphid abundance data plotted against geographical distance $(D)$ between two sampling locations; $\textbf{(A)}$ Spearman correlation vs. $D$, $\textbf{(B)}$ Kendall correlation vs. $D$, $\textbf{(C)}$ $\cor_l-\cor_u$ vs. $D$, $\textbf{(D)}$ $\Ps_l-\Ps_u$ vs. $D$, $\textbf{(E)}$ $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all (10 $\times$ 10 locations) taken pairwise. \label{fig_aphid_count}}
\end{center}
\end{figure}

We computed Spearman and Kendall correlation along with our three non-parametric statistics ($\cor_l-\cor_u$, $\Ps_l-\Ps_u$, $\Dsq_u-\Dsq_l$) as described in Sec. \ref{NPA} for  green spruce aphid abundance data taken at all $10$ $\times$ $10$ location pairs (code given in [`NonParamStat.R`](https://github.com/sghosh89/BIVAN/blob/master/NonParamStat.R)). We also constructed a $10$ $\times$ $10$ matrix using `gcdist` from `ncf` package where each element in that matrix represented the geographical distance between any two selected locations. 
Figure \ref{fig_aphid_count} presented plots for **(A)** Spearman, **(B)** Kendall, **(C)** $\cor_l-\cor_u$, **(D)** $\Ps_l-\Ps_u$ and **(E)** $\Dsq_u-\Dsq_l$ statistics against the geographical distance for all selected sampling location pairs. With increasing the distance *D*, the Spearman and Kendall correlation (hence the synchrony among time series data) between the location pairs decreased as expected. But one cannot conclude the tail dependence of that synchrony from Figure \ref{fig_aphid_count} **(A)** or **(B)**, whereas **(C - E)** clearly showed the lower tail dependence with most of the data points lied in the positive quadrant as described before in Sec. \ref{NPA}.

@@

@@

The model-averaged (averaging performed using AIC weights) lower-tail dependence statistic and 
the model-averaged (again, AIC based) upper-tail dependence statistic are in 
Tables \ref{tab_ff_LTdep_AICw} and \ref{tab_ff_UTdep_AICw}, respectively. These values were exclusively positive, thereby differing from what a normal copula would give (i.e., $0$), and answering the second part of question 1 for these data - these data have greater tail dependence (lower and upper) than would be expected from a normal-copula null hypothesis.

@@

<!--Shya, can you please organize these following plots into one plot with mutliple panels? Once that is done, please add some text describing these results.-->
\begin{figure}[!h]
\begin{center}
\textbf{\;\;\;\;\;\;\;\ (A) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (B)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Spearman_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Kendall_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (C) \;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;\ (D)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Corl-Coru_vs_D.pdf}
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_Pl-Pu_vs_D.pdf}\\
\textbf{\;\;\;\;\;\;\;\ (E)} \\
\includegraphics[width=2in]{./Results/stat_results/stat_aphid_ff/Sp_11_D2u-D2l_vs_D.pdf}
\caption{Non-parametric tail statistics results for leaf-curling plum aphid's first flight date data plotted against geographical distance $(D)$ between two sampling locations; $\textbf{(A)}$ Spearman correlation vs. $D$, $\textbf{(B)}$ Kendall correlation vs. $D$, $\textbf{(C)}$ $\cor_l-\cor_u$ vs. $D$, $\textbf{(D)}$ $\Ps_l-\Ps_u$ vs. $D$, $\textbf{(E)}$ $\Dsq_u-\Dsq_l$ vs. $D$ plotted for all (10 $\times$ 10 locations) taken pairwise. \label{fig_aphid_ff}}
\end{center}
\end{figure}

Figure \ref{fig_aphid_ff} represented plots for **(A)** Spearman correlation, **(B)** Kendall correlation, **(C)** $\cor_l-\cor_u$, **(D)** $\Ps_l-\Ps_u$ and **(E)** $\Dsq_u-\Dsq_l$ statistics, computed on leaf-curling plum aphid's first flight date data, against the geographical distance for all selected sampling location pairs. Likewise in Figure \ref{fig_aphid_count}, with increasing the distance *D*, the Spearman and Kendall correlation (hence the synchrony among time series data) between the location pairs decreased as expected. But here in contrast, Figure \ref{fig_aphid_ff}  **(C - E)** clearly showed the upper tail dependence with most of the data points lied in the negative quadrant as described before in Sec. \ref{NPA}.

Mean values of our statistics ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_l$, $\Dsq_u$, 
$\cor_l-\cor_u$, $\Ps_l-\Ps_u$, $\Dsq_u-\Dsq_l$), as well as mean Kendall and Spearman 
correlations, were 
computed across all pairs of sampling locations, and confidence intervals of these means were 
computed via a spatial
resampling scheme, as described in Methods (Table \ref{tab_ff_resamp}).
Confidence intervals of
$\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_l$, and $\Dsq_u$ always excluded 
zero and mean values were positive,
indicating tail dependence.
Confidence intervals of $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, $\Dsq_u-\Dsq_l$ also always 
exluded $0$ and were negative, indicating asymmetry of tail dependence, a feature 
that data with normal copula 
structure do not have, providing further evidence answering the third part of question 1.
The contrast here with the analogous results for abundances of the green spruce aphid is 
again illuminating.

@@
